---
title: "MECP2 Analysis"
author: "Andrew Willems and Tian Hong"
date: "5/12/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objective
We are doing  analysis on the new set of cohorts from the Krishnan lab for MECP2. First, we use intraclass correlation coefficient (ICC) values of the Cohort, Cell type, Cell number, and Image variables to determine if we need to build linear mixed effects models. After investigating if we need LMEs we then create heat maps of the MECP2 data. We compare the differences in means between the various conditions.

## Step One
Load needed packages. `effectsize` is used to calculate the effect sizes of the differences in our various conditions/treatments. `ggforce` is used to make the sina plots. `ggpubr` is for the grouped plot support. `ggsignif` is used to add statistical results to ggplot plots. `gt` is used for making the nice tables. `ICC` is used to calculate the intraclass correlation coefficient to tell us if we can treat our predictors (variables) as independent or not. `magrittr` is a package that allows us to use pipes (%>%) in our code. `mclust` allows us to build Gaussian mixture models (GMMs) and calculate the mean intensity of the neurons of interest. `modelsummary` allows us to make our linear mixed effects (lme) model output more professional looking. `nlme` is the package that performs the linear mixed effects (lme) model fits. `rstatix` is used to do the pairwise t-tests and p-value correction. `tidyverse` is used for data manipulation. `webshot` is used to save our gt tables as .png files.

```{r message=FALSE, echo=FALSE}
#Loading needed packages
library(effectsize)
library(ggforce)
library(ggpubr)
library(ggsignif)
library(gt)
library(ICC)
library(magrittr)
library(mclust)
library(modelsummary)
library(nlme)
library(rstatix)
library(tidyverse)
library(webshot)
```


## Step Two
Load the data and make separate data frames that are comprised of only left or right hemisphere data. The warning here is okay. When I make all columns numeric it introduces some NAs because not all columns have the same number of rows (some just have no data in that row and therefore they get an NA). I fill those NAs in with a 0. 
```{r tidy=TRUE, tidy.opts=list(arrow=TRUE, indent=2), echo=FALSE, results='hide', eval=TRUE, warning=FALSE}
#Loading the data
setwd("~/Documents/PhD Program/Hong Lab/Projects/Krishnan-lab-Analysis/Data")
mecp2_data <- read.csv("mecp2_raw_histogram_data.csv", sep = ",")
mecp2_metadata_6wk <- mecp2_data[1:6,1:380]
mecp2_metadata_12wk <- mecp2_data[1:6,381:816]
mecp2_intensity <- mecp2_data[7:2164,2:817]
mecp2_intensity_6wk <- mecp2_intensity[,1:380]
mecp2_intensity_12wk <- mecp2_intensity[,381:816]

mecp2_intensity_6wk <- apply(mecp2_intensity_6wk, 2, as.numeric)
mecp2_intensity_12wk <- apply(mecp2_intensity_12wk, 2, as.numeric)

mecp2_intensity_6wk[is.na(mecp2_intensity_6wk)] <- 0
mecp2_intensity_12wk[is.na(mecp2_intensity_12wk)] <- 0

mecp2_data_processed_6wk <- data.frame(Cell_type=as.character(mecp2_metadata_6wk[1,]),
                                   Cohort=as.character(mecp2_metadata_6wk[2,]),
                                   Condition=as.character(mecp2_metadata_6wk[3,]),
                                   Hemisphere=as.character(mecp2_metadata_6wk[4,]),
                                   Image=as.character(mecp2_metadata_6wk[5,]),
                                   Cell_number=as.character(mecp2_metadata_6wk[6,]))


mecp2_data_processed_12wk <- data.frame(Cell_type=as.character(mecp2_metadata_12wk[1,]),
                                   Cohort=as.character(mecp2_metadata_12wk[2,]),
                                   Condition=as.character(mecp2_metadata_12wk[3,]),
                                   Hemisphere=as.character(mecp2_metadata_12wk[4,]),
                                   Image=as.character(mecp2_metadata_12wk[5,]),
                                   Cell_number=as.character(mecp2_metadata_12wk[6,]))



mecp2_data_processed_6wk <- mecp2_data_processed_6wk[2:817,]
mecp2_data_processed_12wk <- mecp2_data_processed_12wk[2:817,]

head(mecp2_data_processed_6wk)
head(mecp2_data_processed_12wk)
dim(mecp2_data_processed_6wk)
dim(mecp2_data_processed_12wk)
```

## Step Three: Building Gaussian Mixed Model (GMMs) for all of our data
Six week old data. We have a single mean intensity calculated for each sample
```{r message=FALSE, fig.show='hide', echo=FALSE, eval=TRUE, warning=FALSE}
#Doing density estimates for each of the columns of our data frame to get 
#means for further analysis for 6wk data
gmm_mod_6wk <- apply(mecp2_intensity_6wk, 2, densityMclust, G = 1, 
                     modelNames=c("E", "V"))
```

Twelve week old data. We have a single mean intensity calculated for each sample
```{r message=FALSE, fig.show='hide', echo=FALSE, eval=TRUE, warning=FALSE}
#Doing density estimates for each of the columns of our data frame to get 
#means for further analysis for 12wk data
gmm_mod_12wk <- apply(mecp2_intensity_12wk, 2, densityMclust, G = 1,
                      modelNames=c("E", "V"))
```


## Step Four: Now plotting and then saving all of the density plots for 6 week year old data 
```{r echo=FALSE, message=FALSE, eval=TRUE}
#Plotting the results and saving the mean to do more analysis later
setwd("~/Documents/PhD Program/Hong Lab/Projects/Krishnan-lab-Analysis/Figures/Mecp2_figures")
first_means_6wk <- rep(0, 816)
second_means_6wk <- rep(0, 816)
all_plots <- list()
counter <- 1
for(gm in gmm_mod_6wk){
  current_mod <- gm
  first_means_6wk[counter] <- current_mod$parameters$mean[1]
  
  current_mod_ggplot <- as.data.frame(current_mod$density)
  colnames(current_mod_ggplot) <- "density"
  current_mod_ggplot$mean <- first_means_6wk[counter]
  density_plot <- ggplot(data = current_mod_ggplot, aes(x=density)) +
    geom_density(color="blue",
                 fill= "#87ceeb",
                 alpha=0.8) +
    theme(panel.background = element_blank())+
    xlab("Intensity")+ ylab("Density")
  len <- length(all_plots)
  all_plots[[len+1]] <- density_plot
  
  ggsave(filename = paste0("density_plot_mecp2_6wk_", len, ".png"), device = "png",
         dpi = 300, height = 12, width = 12, unit= "cm", plot = density_plot)
  counter <- counter + 1
}

```



## Plotting and saving for 12 week old data
```{r echo=FALSE, message=FALSE, eval=TRUE}
#Plotting the results and saving the mean to do more analysis later
setwd("~/Documents/PhD Program/Hong Lab/Projects/Krishnan-lab-Analysis/Figures/Mecp2_figures")
first_means_12wk <- rep(0, 816)
second_means_12wk <- rep(0, 816)
all_plots <- list()
counter <- 1
for(gm in gmm_mod_12wk){
  current_mod <- gm
  first_means_12wk[counter] <- current_mod$parameters$mean[1]
  
  current_mod_ggplot <- as.data.frame(current_mod$density)
  colnames(current_mod_ggplot) <- "density"
  current_mod_ggplot$mean <- first_means_12wk[counter]
  density_plot <- ggplot(data = current_mod_ggplot, aes(x=density)) +
    geom_density(color="blue",
                 fill= "#87ceeb",
                 alpha=0.8) +
    theme(panel.background = element_blank())+
    xlab("Intensity")+ ylab("Density")
  len <- length(all_plots)
  all_plots[[len+1]] <- density_plot
  
  ggsave(filename = paste0("density_plot_mecp2_12wk_", len, ".png"), device = "png",
         dpi = 300, height = 12, width = 12, unit= "cm", plot = density_plot)
  counter <- counter + 1
}
```


## Step Five: Adding the means of the GMM to our overall data frames
```{r, echo=FALSE}
#Now appending the mean to the other metadata for this MECP2 data set for the
#6 week and 12 week data frames
mecp2_data_processed_6wk$Mean <- first_means_6wk

mecp2_data_processed_6wk$Time <- rep("6 wk",
                                     times=nrow(mecp2_data_processed_6wk))
head(mecp2_data_processed_6wk)



mecp2_data_processed_12wk$Mean <- first_means_12wk
mecp2_data_processed_12wk$Time <- rep("12 wk",
                                      times=nrow(mecp2_data_processed_12wk))
head(mecp2_data_processed_12wk)
```


Now sub-setting our data frame to just NH and NW and then relabeling them as Het or WT. Finally, we factor them in the same order seen in the plot in the pre-print
```{r, echo=FALSE}
mecp2_data_processed_6wk_simp <- mecp2_data_processed_6wk
mecp2_data_processed_6wk_simp <- filter(mecp2_data_processed_6wk_simp,
                                        Condition=="NH" | Condition=="NW")

mecp2_data_processed_6wk_simp_pos <- filter(mecp2_data_processed_6wk_simp, Cell_type=="PNN-pos")
mecp2_data_processed_6wk_simp_neg <- filter(mecp2_data_processed_6wk_simp, Cell_type=="PNN-neg")

mecp2_data_processed_6wk_simp_neg$Condition <- gsub(x = mecp2_data_processed_6wk_simp_neg$Condition, pattern = "NH", replacement = "Het")
mecp2_data_processed_6wk_simp_neg$Condition <- gsub(x = mecp2_data_processed_6wk_simp_neg$Condition, pattern = "NW", replacement = "WT")
mecp2_data_processed_6wk_simp_pos$Condition <- gsub(x = mecp2_data_processed_6wk_simp_pos$Condition, pattern = "NH", replacement = "Het")
mecp2_data_processed_6wk_simp_pos$Condition <- gsub(x = mecp2_data_processed_6wk_simp_pos$Condition, pattern = "NW", replacement = "WT")


mecp2_data_processed_6wk_simp_neg$Condition <- factor(mecp2_data_processed_6wk_simp_neg$Condition, levels = c("WT", "Het"))
mecp2_data_processed_6wk_simp_pos$Condition <- factor(mecp2_data_processed_6wk_simp_pos$Condition, levels = c("WT", "Het"))
```

Doing the same for 12 week old data
```{r, echo=FALSE}
mecp2_data_processed_12wk_simp <- mecp2_data_processed_12wk

mecp2_data_processed_12wk_simp <- filter(mecp2_data_processed_12wk_simp,
                                        Condition=="NH" | Condition=="NW")

mecp2_data_processed_12wk_simp_pos <- filter(mecp2_data_processed_12wk_simp, Cell_type=="PNN-pos")
mecp2_data_processed_12wk_simp_neg <- filter(mecp2_data_processed_12wk_simp, Cell_type=="PNN-neg")

mecp2_data_processed_12wk_simp_neg$Condition <- gsub(x = mecp2_data_processed_12wk_simp_neg$Condition, pattern = "NH", replacement = "Het")
mecp2_data_processed_12wk_simp_neg$Condition <- gsub(x = mecp2_data_processed_12wk_simp_neg$Condition, pattern = "NW", replacement = "WT")
mecp2_data_processed_12wk_simp_pos$Condition <- gsub(x = mecp2_data_processed_12wk_simp_pos$Condition, pattern = "NH", replacement = "Het")
mecp2_data_processed_12wk_simp_pos$Condition <- gsub(x = mecp2_data_processed_12wk_simp_pos$Condition, pattern = "NW", replacement = "WT")


mecp2_data_processed_12wk_simp_neg$Condition <- factor(mecp2_data_processed_12wk_simp_neg$Condition, levels = c("WT", "Het"))
mecp2_data_processed_12wk_simp_pos$Condition <- factor(mecp2_data_processed_12wk_simp_pos$Condition, levels = c("WT", "Het"))
```


Now doing all the statistical analysis and plotting for the PV Nuclei containing samples
```{r, echo=FALSE}
mecp2_6_12_pos <- bind_rows(mecp2_data_processed_6wk_simp_pos, mecp2_data_processed_12wk_simp_pos)

#Not needed to be run every time since we have already saved the file
saveRDS(mecp2_6_12_pos,
        file = "~/Documents/PhD Program/Hong Lab/Projects/Krishnan-lab-Analysis/Data/mecp2_6_12_pos.rds")

#Performing all KW tests for the overall model and then uncorrected Dunn's tests
#for each of the particular pairwise comparisons in line with collaborator's
#previous analysis

overall_test <- mecp2_6_12_pos %>% kruskal_test(formula = Mean~Time)

example_of_pwc <- mecp2_6_12_pos %>% group_by(Time) %>% filter(Time=="6 wk") %>%
  dunn_test(formula = Mean~Condition, detailed = TRUE, p.adjust.method = "none")

six_wk_comp <- mecp2_6_12_pos %>% group_by(Time) %>% filter(Time=="6 wk") %>%
  dunn_test(formula = Mean~Condition, detailed = TRUE, p.adjust.method = "none")

twelve_wk_comp <- mecp2_6_12_pos %>% group_by(Time) %>% filter(Time=="12 wk") %>%
  dunn_test(formula = Mean~Condition, detailed = TRUE, p.adjust.method = "none")

#6 week WT v. 6 week Het
wt_v_wt_comp <- mecp2_6_12_pos %>% group_by(Condition) %>% filter(Condition=="WT") %>%
  dunn_test(formula = Mean~Time, detailed = TRUE, p.adjust.method = "none")

#6 week Het v. 12 week Het
het_v_het_comp <- mecp2_6_12_pos %>% group_by(Condition) %>% filter(Condition=="Het") %>%
  dunn_test(formula = Mean~Time, detailed = TRUE, p.adjust.method = "none")


#Effect size and effects size interpretation
overall_effect_size <- kruskal_effsize(data = mecp2_6_12_pos, 
                                       formula = Mean~Time, ci = TRUE)

six_wk_eff_size_df <- mecp2_6_12_pos %>% group_by(Time) %>% filter(Time=="6 wk")
six_wk_eff_size <- hedges_g(data = six_wk_eff_size_df, x = Mean~Condition)



twelve_wk_eff_size_df <- mecp2_6_12_pos %>% group_by(Time) %>% filter(Time=="12 wk")
twelve_wk_eff_size <- hedges_g(data = twelve_wk_eff_size_df, x = Mean~Condition)



wt_v_wt_eff_size_df <- mecp2_6_12_pos %>% group_by(Condition) %>% filter(Condition=="WT")
wt_v_wt_eff_size <- hedges_g(data = wt_v_wt_eff_size_df, x = Mean~Time)


het_v_het_eff_size_df <- mecp2_6_12_pos %>% group_by(Condition) %>% filter(Condition=="Het")
het_v_het_eff_size <- hedges_g(data = het_v_het_eff_size_df, x = Mean~Time)

overall_test_label <- create_test_label(description = "Kruskal-Wallis",
                                        statistic.text = quote(italic(chi)^2),
                                        statistic = 0.151, p = "0.697",
                                        parameter = "1", n = 188,
                                        effect.size.text = quote(italic(eta)^2),
                                        effect.size = -0.00456, detailed = TRUE,
                                        type = "expression")


#Now back to doing plotting stuff
mecp2_6_12_pos$Time <- factor(mecp2_6_12_pos$Time, levels = c("6 wk", "12 wk"))

mecp2_6_12_pos$Combo <- paste0(mecp2_6_12_pos$Condition,"_", mecp2_6_12_pos$Time)
mecp2_6_12_pos$Combo <- factor(mecp2_6_12_pos$Combo, levels = c("WT_6 wk",
                                                                "Het_6 wk", 
                                                                "WT_12 wk",
                                                                "Het_12 wk"))


#Plot
total_plot <- ggplot(aes(x=Combo,y=Mean, fill=Condition), data = mecp2_6_12_pos)+
  geom_violin()+ theme(panel.background = element_blank(),
                       plot.title = element_text(hjust = 0.5, face = "bold"),
                       axis.title = element_text(face = "bold"),
                       axis.text = element_text(face = "bold"),
                       legend.position = "none")+
  ylab("Mean MECP2 Intensity (a.u.)")+
  xlab("")+
  geom_sina(seed=123)+
  ggtitle("PV Nuclei using PNN-pos cell type")+
  geom_signif(y_position = c(4300, 3870), xmin = c(1.0,3.0), xmax = c(2.0,4.0),
              annotations = c("ns", "ns"), tip_length = 0)+
  geom_signif(y_position = 4500, xmin = 1.0, xmax = 3.0, annotations = "ns",
              tip_length = 0)+
  geom_signif(y_position = 4200, xmin = 2.0, xmax = 4.0, annotations = "ns",
              tip_length = 0)+
  labs(
    subtitle = overall_test_label,
    caption = get_pwc_label(example_of_pwc)
    )


total_plot <- total_plot + scale_x_discrete(breaks = c("WT_6 wk","Het_6 wk",
                                                       "WT_12 wk", "Het_12 wk"),
                                            labels = c("WT \n(n = 47)", 
                                                       "Het \n(n = 35)", 
                                                       "WT \n(n = 59)", 
                                                       "Het \n(n = 47)"))

total_plot <- total_plot + stat_summary(fun=mean, geom="point", shape=23,
                                        size=5, color="white", fill="white")

total_plot_pos <- total_plot

total_plot_pos
```




