---
title: "111722_pnn_analysis"
author: "Andrew Willems and Tian Hong"
date: "2023-01-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = "~/Documents/Work/Phd_program/hong_lab/Projects/rett_syndrome/")
```

## Objective: Analyze cohort 111722 PNN data for collaborators

## Step 1: Load needed packages and setting various options
```{r loading packages}
suppressMessages(library(circlize))
suppressMessages(library(ComplexHeatmap))
suppressMessages(library(cowplot))
suppressMessages(library(ggplot2))
suppressMessages(library(ggpubr))
suppressMessages(library(ggsignif))
suppressMessages(library(gplots))
suppressMessages(library(grid))
suppressMessages(library(gt))
suppressMessages(library(gtable))
suppressMessages(library(ICC))
suppressMessages(library(matrixcalc))
suppressMessages(library(mclust))
suppressMessages(library(rstatix))
suppressMessages(library(tidyverse))
suppressMessages(library(webshot2))
```

## Step 2: Load in data
```{r loading data}
chs_rm <- "n"
gmm_n <- 2
using_mean1 <- FALSE

pnn_data <- read.csv("Data/111722_pnn_histogram_data/111722_pnn_histogram_data_complete.csv", sep = ",")
meta_data <- pnn_data[1:10, 1:2981]
meta_data <- t(meta_data)
colnames(meta_data) <- meta_data[1, ]
meta_data <- as.data.frame(meta_data)
meta_data <- meta_data[2:2981, ]
meta_data$author <- rownames(meta_data)[2:2981]
rownames(meta_data) <- 1:nrow(meta_data)
colnames(meta_data) <- c("date", "cohort", "condition", "coordinates", "hemisphere", "subregion", "rotation_x", "rotation_y", "z_position", "area", "author")
meta_data$cohort <- gsub(pattern = "#", replacement = "", x = meta_data$cohort)
meta_data$author <- gsub(pattern = "[0123456789]", replacement = "", x = meta_data$author)
meta_data$author <- gsub(pattern = "LD...", replacement = "LD", x = meta_data$author)
meta_data$author <- gsub(pattern = "JM...", replacement = "JM", x = meta_data$author)
meta_data$author <- gsub(pattern = "RS...", replacement = "RS", x = meta_data$author)
meta_data$author <- gsub(pattern = "LD.", replacement = "LD", x = meta_data$author)
meta_data$author <- gsub(pattern = "JM.", replacement = "JM", x = meta_data$author)
meta_data$author <- gsub(pattern = "RS.", replacement = "RS", x = meta_data$author)
expr_data <- pnn_data[11:266, 2:2981]
expr_data <- t(expr_data)
expr_data <- as.data.frame(expr_data)
colnames(expr_data) <- paste0("ch_", 1:ncol(expr_data))
if (chs_rm == "n") {
  all_data <- bind_cols(meta_data, expr_data)
} else {
  all_data <- bind_cols(meta_data, expr_data)
  all_data <- subset(all_data, select = c(date:author, ch_10:ch_256))
}
```


## Step 3: Mclust
```{r mclust analysis}
mods <- list()
mods_sum <- list()
for (s in unique(all_data$subregion)) {
  current_region <- filter(all_data, subregion == s)
  for (r in 1:nrow(current_region)) {
    mod <- densityMclust(as.numeric(as.vector(unlist(current_region[r, 12:ncol(all_data)]))), modelNames = "E", G = gmm_n, plot = FALSE)
    mods[[r]] <- mod
    summary_mod <- summary(mod, parameters = TRUE)
    mods_sum[[r]] <- summary_mod
    if (gmm_n == 1 & chs_rm == "n") {
      icc_df <- data.frame(
        cohort = current_region[r, "cohort"],
        condition = current_region[r, "condition"],
        hemisphere = current_region[r, "hemisphere"],
        subregion = current_region[r, "subregion"],
        area = current_region[r, "area"],
        author = current_region[r, "author"],
        coordinates = current_region[r, "coordinates"],
        rotation_x = current_region[r, "rotation_x"],
        rotation_y = current_region[r, "rotation_y"],
        mean_1 = mod$parameters$mean[[1]],
        model_name = mod$modelName,
        n = mod$n,
        d = mod$d,
        num_of_clusters = mod$G,
        intensity = as.numeric(as.vector(unlist(current_region[r, 12:ncol(all_data)])))
      )
      write.csv(icc_df, file = paste0("Outputs/pnn_analysis/density_data/one_cluster/no_chs_removed/sample_", r, "_", s, ".csv"))
    } else if (gmm_n == 2 & chs_rm == "n") {
      icc_df <- data.frame(
        cohort = current_region[r, "cohort"],
        condition = current_region[r, "condition"],
        hemisphere = current_region[r, "hemisphere"],
        subregion = current_region[r, "subregion"],
        area = current_region[r, "area"],
        author = current_region[r, "author"],
        coordinates = current_region[r, "coordinates"],
        rotation_x = current_region[r, "rotation_x"],
        rotation_y = current_region[r, "rotation_y"],
        mean_1 = mod$parameters$mean[[1]],
        mean_2 = mod$parameters$mean[[2]],
        model_name = mod$modelName,
        n = mod$n,
        d = mod$d,
        num_of_clusters = mod$G,
        intensity = as.numeric(as.vector(unlist(current_region[r, 12:ncol(all_data)])))
      )
      write.csv(icc_df, file = paste0("Outputs/pnn_analysis/density_data/two_cluster/no_chs_removed/sample_", r, "_", s, ".csv"))
    } else if (gmm_n == 2 & chs_rm == "y") {
      icc_df <- data.frame(
        cohort = current_region[r, "cohort"],
        condition = current_region[r, "condition"],
        hemisphere = current_region[r, "hemisphere"],
        subregion = current_region[r, "subregion"],
        area = current_region[r, "area"],
        author = current_region[r, "author"],
        coordinates = current_region[r, "coordinates"],
        rotation_x = current_region[r, "rotation_x"],
        rotation_y = current_region[r, "rotation_y"],
        mean_1 = mod$parameters$mean[[1]],
        mean_2 = mod$parameters$mean[[2]],
        model_name = mod$modelName,
        n = mod$n,
        d = mod$d,
        num_of_clusters = mod$G,
        intensity = as.numeric(as.vector(unlist(current_region[r, 12:ncol(all_data)])))
      )
      write.csv(icc_df, file = paste0("Outputs/pnn_analysis/density_data/two_cluster/chs_removed/sample_", r, "_", s, ".csv"))
    } else if (gmm_n == 1 & chs_rm == "y") {
      icc_df <- data.frame(
        cohort = current_region[r, "cohort"],
        condition = current_region[r, "condition"],
        hemisphere = current_region[r, "hemisphere"],
        subregion = current_region[r, "subregion"],
        area = current_region[r, "area"],
        author = current_region[r, "author"],
        coordinates = current_region[r, "coordinates"],
        rotation_x = current_region[r, "rotation_x"],
        rotation_y = current_region[r, "rotation_y"],
        mean_1 = mod$parameters$mean[[1]],
        model_name = mod$modelName,
        n = mod$n,
        d = mod$d,
        num_of_clusters = mod$G,
        intensity = as.numeric(as.vector(unlist(current_region[r, 12:ncol(all_data)])))
      )
      write.csv(icc_df, file = paste0("Outputs/pnn_analysis/density_data/one_cluster/chs_removed/sample_", r, "_", s, ".csv"))
    }

    if (gmm_n == 1 & chs_rm == "n") {
      plot_title <- paste(s, "| E |", mod$G, "Cluster | ", r)
      my_filname <- paste0(s, "_", r, ".png")
      my_path <- paste0("Outputs/pnn_analysis/density_plots/png/one_cluster_gmm/no_chs_removed/")
    } else if (gmm_n == 1 & chs_rm == "y") {
      plot_title <- paste(s, "| E |", mod$G, "Cluster | ", r, "Chs. 1-9 Rm")
      my_filname <- paste0(s, "_", r, ".png")
      my_path <- paste0("Outputs/pnn_analysis/density_plots/png/one_cluster_gmm/chs_removed/")
    } else if (gmm_n == 2 & chs_rm == "n") {
      plot_title <- paste(s, "|", mod$modelName, "|", mod$G, "Clusters | ", r)
      my_filname <- paste0(s, "_", r, ".png")
      my_path <- paste0("Outputs/pnn_analysis/density_plots/png/two_cluster_gmm/no_chs_removed/")
    } else if (gmm_n == 2 & chs_rm == "y") {
      plot_title <- paste(s, "|", mod$modelName, "|", mod$G, "Clusters | ", r, "Chs. 1-9 Rm")
      my_filname <- paste0(s, "_", r, ".png")
      my_path <- paste0("Outputs/pnn_analysis/density_plots/png/two_cluster_gmm/chs_removed/")
    }

    p <- ggplot(data = icc_df, aes(x = intensity)) +
      geom_density(fill = "lightblue", color = "darkblue") +
      theme(
        plot.title = element_text(hjust = 0.5, size = 28, face = "bold"),
        axis.title = element_text(size = 22, face = "bold"),
        panel.background = element_blank()
      ) +
      xlab("Intensity") +
      ylab("Density") +
      ggtitle(paste(plot_title))

    ggsave(
      path = my_path, filename = my_filname,
      plot = print(p), device = "png", dpi = 600, width = 9,
      height = 9, units = "in"
    )
  }
  mods <- list()
  mods_sum <- list()
}
```

```{r icc dataframes}
if (gmm_n == 1 & chs_rm == "n") {
  all_files <- list.files("Outputs/pnn_analysis/density_data/one_cluster/no_chs_removed/")
  files_list <- vector("list", length = length(all_files))

  for (f in all_files) {
    current_file <- read.csv(paste0("Outputs/pnn_analysis/density_data/one_cluster/no_chs_removed/", f))
    files_list[[f]] <- current_file
  }
  icc_df <- bind_rows(files_list)
  icc_df <- subset(icc_df, select = c("condition", "hemisphere", "subregion", "author", "rotation_x", "area", "rotation_y", "mean_1"))
} else if (gmm_n == 1 & chs_rm == "y") {
  all_files <- list.files("Outputs/pnn_analysis/density_data/one_cluster/chs_removed/")
  files_list <- vector("list", length = length(all_files))

  for (f in all_files) {
    current_file <- read.csv(paste0("Outputs/pnn_analysis/density_data/one_cluster/chs_removed/", f))
    files_list[[f]] <- current_file
  }
  icc_df <- bind_rows(files_list)
  icc_df <- subset(icc_df, select = c("condition", "hemisphere", "subregion", "author", "rotation_x", "area", "rotation_y", "mean_1"))
} else if (gmm_n == 2 & chs_rm == "n") {
  all_files <- list.files("Outputs/pnn_analysis/density_data/two_cluster/no_chs_removed/")
  files_list <- vector("list", length = length(all_files))

  for (f in all_files) {
    current_file <- read.csv(paste0("Outputs/pnn_analysis/density_data/two_cluster/no_chs_removed/", f))
    files_list[[f]] <- current_file
  }
  icc_df <- bind_rows(files_list)
  icc_df <- subset(icc_df, select = c("condition", "hemisphere", "subregion", "author", "rotation_x", "area", "rotation_y", "mean_1", "mean_2"))
} else if (gmm_n == 2 & chs_rm == "y") {
  all_files <- list.files("Outputs/pnn_analysis/density_data/two_cluster/chs_removed/")
  files_list <- vector("list", length = length(all_files))

  for (f in all_files) {
    current_file <- read.csv(paste0("Outputs/pnn_analysis/density_data/two_cluster/chs_removed/", f))
    files_list[[f]] <- current_file
  }
  icc_df <- bind_rows(files_list)
  icc_df <- subset(icc_df, select = c("condition", "hemisphere", "subregion", "author", "rotation_x", "area", "rotation_y", "mean_1", "mean_2"))
}
```

## Step 4: ICC Analysis
```{r icc analysis function}
icc_analysis <- function(data = all_data, subset_data = FALSE, subset_var = NULL, subset_val = NULL, dependent_var = "mean_2", icc_title = "ICC Analysis", icc_filename = "table", icc_path = "Outputs/pnn_analysis/icc_data/gt_tables/") {
  iccs <- list()
  returns <- list()

  if (subset_data == TRUE) {
    data <- filter(data, {{ subset_var }} == {{ subset_val }})
  }

  for (c in colnames(data)) {
    if (c == {{ dependent_var }}) {
      print("This is the dependent variable. We are skipping it")
      next
    } else {
      icc <- ICCbare(x = {{ c }}, y = {{ dependent_var }}, data = data)
      iccs[[c]] <- icc
    }
  }

  # Making a data frame
  icc_df_sub <- bind_cols(iccs)

  # Making that data frame a nicer looking table
  gt_icc <- gt(icc_df)
  gt_icc <- gt_icc %>%
    tab_header(
      title = icc_title
    ) %>%
    cols_align(
      align = "center",
      columns = c(colnames(icc_df_sub))
    ) %>%
    tab_options(heading.align = "center")


  gtsave(gt_icc, filename = paste0(icc_filename), path = paste0(icc_path))

  # Adding the outputs we want to return
  returns[["iccs"]] <- iccs

  return(returns)
}

icc_output <- suppressWarnings(icc_analysis(data = all_data, subset_data = FALSE, subset_var = NULL, subset_val = NULL, dependent_var = "mean_2", icc_title = "111722 2 Cluster Mean 2 ICC", icc_filename = "111722_all_vars_dep_var_mean_2_two_cluster_gmm.png", icc_path = "Outputs/pnn_analysis/gt_tables/"))
```
## Step 4b: P-value Analysis
```{r p-value analysis}
rate_of_false_positives <- rep(0, 3)
rate_of_false_positives[1] <- 1 - (1 - 0.05)^4
rate_of_false_positives[2] <- 1 - (1 - 0.01)^4
rate_of_false_positives[3] <- 1 - (1 - 0.001)^4

p_values <- c(0.05, 0.01, 0.001)
fp_table <- data.frame(p_values, rate_of_false_positives)
colnames(fp_table) <- c("P-value", "False Positive Rate")
fp_table <- gt(fp_table)
fp_table <- fp_table %>%
  tab_header(
    title = "Uncorrected P-value Analysis"
  ) %>%
  cols_align(
    align = "center",
    columns = c("P-value", "False Positive Rate")
  ) %>%
  fmt_percent(
    columns = "False Positive Rate",
    decimals = 1
  )

gtsave(fp_table, path = "Outputs/pnn_analysis/p_value_analysis/", filename = "p_value_analysis.png")
```



## ComplexHeatmap
```{r complex heatmap}
test_mat <- matrix(data = 0, nrow = 6, ncol = 6, dimnames = list(c("NW", "NH", "SW P0-P1", "SW P0-P5", "SH P0-P1", "SH P0-P5"), c("NW", "NH", "SW P0-P1", "SW P0-P5", "SH P0-P1", "SH P0-P5")))

comparisons <- list()
my_estimates <- list()
my_estimates_low <- list()
my_estimates_high <- list()
my_estimates_low_mod <- list()
my_sigs <- list()
my_t_tests <- list()
plots <- list()

for (c in colnames(test_mat)) {
  for (r in rownames(test_mat)) {
    comparisons[[paste0(r, "_", c)]] <- paste0(r, "_", c)
  }
}

for (s in unique(icc_df$subregion)) {
  current_df <- filter(icc_df, subregion == s)
  for (c in comparisons) {
    cond_x <- strsplit(c, "_")
    cond_y <- cond_x[[1]][2]
    cond_x <- cond_x[[1]][1]
    current_df_sub <- filter(current_df, condition == cond_x | condition == cond_y)
    if (length(table(current_df_sub$condition)) < 2) {
      current_comp <- c()
      current_comp$estimate <- NA
      current_comp$p.adj.signif <- ""
      my_estimates[[paste0(cond_x, cond_y)]] <- current_comp$estimate
      my_sigs[[paste0(cond_x, cond_y)]] <- current_comp$p.adj.signif
      my_t_tests[[paste0(cond_x, "_", cond_y)]] <- c(0, 0, 0, "mean_2", names(table(current_df_sub$condition)), names(table(current_df_sub$condition)), unname(table(current_df_sub$condition)), unname(table(current_df_sub$condition)), 0, 1, 0, 0, 0, "T-test", "two.sided", 1, "ns")
    } else {
      current_comp <- NULL
      current_comp <- t_test(data = current_df_sub, formula = mean_2 ~ condition, detailed = TRUE, conf.level = 0.999) %>%
        adjust_pvalue(method = "holm") %>%
        add_significance("p.adj")
      my_t_tests[[paste0(cond_x, "_", cond_y)]] <- current_comp
      my_estimates[[paste0(cond_x, "_", cond_y)]] <- current_comp$estimate
      my_sigs[[paste0(cond_x, "_", cond_y)]] <- current_comp$p.adj.signif
    }
  }

  estimates_mat <- do.call("cbind", my_estimates)
  sigs_mat <- do.call("cbind", my_sigs)
  dim(estimates_mat) <- c(6, 6)
  dim(sigs_mat) <- c(6, 6)
  dimnames(estimates_mat) <- list(rownames(test_mat), colnames(test_mat))
  dimnames(sigs_mat) <- list(rownames(test_mat), colnames(test_mat))
  lower_estimates <- lower.triangle(estimates_mat)
  upper_estimates <- upper.triangle(estimates_mat)
  lower_estimates <- lower_estimates * -1
  lower_estimates <- apply(lower_estimates, c(1, 2), as.numeric)
  indicies_to_rep <- which(lower_estimates == 0.000, arr.ind = TRUE)
  indices_to_use_in_upper <- which(upper_estimates != 0.000, arr.ind = TRUE)
  lower_estimates[indicies_to_rep] <- upper_estimates[indices_to_use_in_upper]

  if (s == "MOs") {
    p1 <- Heatmap(matrix = lower_estimates, heatmap_legend_param = list(title = "Difference in Means\n(x-y)"), cluster_rows = FALSE, cluster_columns = FALSE, row_names_side = "left", column_names_centered = TRUE, column_names_rot = 0, row_order = c("SH P0-P5", "SH P0-P1", "SW P0-P5", "SW P0-P1", "NH", "NW"), na_col = "white", row_names_gp = gpar(fontsize = 7, fontface = "bold"), column_names_gp = gpar(fontsize = 7, fontface = "bold"), column_title = paste0(s, " | Mean 2"), cell_fun = function(j, i, x, y, width, height, fill) {
      grid.text(sprintf("%s", sigs_mat[i, j]), x, y, gp = gpar(fontsize = 10))
    }, rect_gp = gpar(color = "black"))
  } else {
    p1 <- Heatmap(matrix = lower_estimates, heatmap_legend_param = list(title = "Difference in Means\n(x-y)"), cluster_rows = FALSE, cluster_columns = FALSE, row_names_side = "left", column_names_centered = TRUE, column_names_rot = 0, row_order = c("SH P0-P5", "SH P0-P1", "SW P0-P5", "SW P0-P1", "NH", "NW"), row_names_gp = gpar(fontsize = 7, fontface = "bold"), na_col = "white", column_names_gp = gpar(fontsize = 7, fontface = "bold"), column_title = paste0(s, " | Mean 2"), cell_fun = function(j, i, x, y, width, height, fill) {
      grid.text(sprintf("%s", sigs_mat[i, j]), x, y, gp = gpar(fontsize = 10))
    }, rect_gp = gpar(color = "black"))
  }




  png(file = paste0("Outputs/pnn_analysis/heatmaps/two_cluster_gmm/mean_2/no_chs_removed/subregion_", s, "_complex_heatmap.png"), units = "in", width = 5, height = 0.3937 * 6 + 0.7423, res = 600)
  p1 <- draw(p1, height = unit(1, "cm") * 6)
  draw(p1, height = unit(1, "cm") * 6)
  dev.off()

  p1 <- grid.grabExpr(draw(p1))
  plots[[s]] <- p1
}
combo_plot <- plot_grid(plotlist = plots, align = "hv", nrow = 5, ncol = 5, labels = "AUTO")
save_plot(filename = "Outputs/pnn_analysis/heatmaps/two_cluster_gmm/mean_2/no_chs_removed/combo_plot_complexheatmap.png", plot = combo_plot, ncol = 5, nrow = 5, base_asp = 1.618, bg = "white")
```


## Step 5: T-test by subregion
### Using mean_1 of 2 cluster model we get only the MOs subregion that appears to exhibit non statsitically significant differences across a decent number of conditions.
### Using a 1 cluster model we get 
```{r t-test analysis}
t_tests <- list()
heatmaps <- list()
heatmaps2 <- list()
returns <- list()


if (gmm_n == 2 & chs_rm == "n" & using_mean1 == FALSE) {
  for (s in unique(icc_df$subregion)) {
    icc_df_sub <- filter(icc_df, subregion == s)
    test <- t_test(
      data = icc_df_sub, formula = mean_2 ~ condition,
      p.adjust.method = "holm", conf.level = 0.999, detailed = TRUE
    )

    # test$group1 <- factor(test$group1, levels = c("NW", "NH", "SW P0-P1", "SW P0-P5", "SH P0-P1", "SH P0-P5"))
    # test$group2 <- factor(test$group2, levels = c("NW", "NH", "SW P0-P1", "SW P0-P5", "SH P0-P1", "SH P0-P5"))

    for (c in unique(icc_df_sub$condition)) {
      test <- rbind(test, c(0, 0, 0, "mean_2", c, c, 0, 0, 0, 0, 0, 0, 0, "T-test", "two.sided", 1, "ns"))
    }

    test[c(1, 2, 3, 7, 8:13, 16)] <- lapply(test[c(1, 2, 3, 7, 8:13, 16)], as.numeric)


    # Heatmap
    mid <- 0
    heatmap1 <- ggplot(data = test, aes(
      x = group1, y = group2,
      fill = estimate
    )) +
      geom_tile() +
      theme(
        plot.title = element_text(size = 12, face = "plain", hjust = 0.5),
        panel.background = element_blank(),
        axis.text.y = element_text(
          size = 7, face = "bold", angle = 90,
          hjust = 0.5
        ),
        axis.text.x = element_text(size = 7, face = "bold"),
        legend.key.height = unit(20, units = "pt")
      ) +
      ggtitle(paste(s, "| Mean 2")) +
      scale_fill_gradient2(low = "blue", mid = "white", high = "red", name = "Difference in means\n(x-y)") +
      xlab("") +
      ylab("") +
      coord_equal() +
      geom_text(aes(label = p.adj.signif))

    heatmap2 <- heatmap1 + coord_flip()



    ggsave(
      plot = print(heatmap1), filename = paste0("Outputs/pnn_analysis/heatmaps/two_cluster_gmm/mean_2/no_chs_removed/", s, "_mean_2_bottom.png"),
      device = "png", width = 6, height = 6, units = "in", dpi = 600
    )

    ggsave(
      plot = print(heatmap2), filename = paste0("Outputs/pnn_analysis/heatmaps/two_cluster_gmm/mean_2/no_chs_removed/", s, "_mean_2_top.png"),
      device = "png", width = 6, height = 6, units = "in", dpi = 600
    )

    t_tests[[s]] <- test
    heatmaps[[paste0(s, "_bottom")]] <- heatmap1
    heatmaps2[[paste0(s, "_top")]] <- heatmap2
    returns[[1]] <- t_tests
    returns[[2]] <- heatmaps
  }


  figure <- ggarrange(
    plotlist = heatmaps, ncol = 5,
    nrow = 5,
    align = "hv",
    common.legend = TRUE,
    legend = "right",
    labels = "AUTO"
  )

  annotated_figure <- annotate_figure(p = figure, top = text_grob("2 Cluster GMM | Mean 2", face = "bold", size = 18))

  ggsave(path = "Outputs/pnn_analysis/heatmaps/two_cluster_gmm/mean_2/no_chs_removed/", filename = "mean_2_2_cluster_gmm_combo_plot.png", plot = annotated_figure, device = "png", width = 20, height = 20, units = "in", dpi = 600, bg = "white")
} else if (gmm_n == 2 & chs_rm == "y" & using_mean1 == FALSE) {
  for (s in unique(icc_df$subregion)) {
    icc_df_sub <- filter(icc_df, subregion == s)
    group_variance <- fligner.test(mean_2 ~ condition, data = icc_df_sub)
    test <- t_test(
      data = icc_df_sub, formula = mean_2 ~ condition,
      p.adjust.method = "holm", conf.level = 0.999, detailed = TRUE
    )

    # Heatmap
    mid <- 0
    heatmap <- ggplot(data = test, aes(
      x = group2, y = group1,
      fill = estimate
    )) +
      geom_tile() +
      theme(
        plot.title = element_text(size = 12, face = "plain", hjust = 0.5),
        panel.background = element_blank(),
        axis.text.y = element_text(
          size = 7, face = "bold", angle = 90,
          hjust = 0.5
        ),
        axis.text.x = element_text(size = 7, face = "bold"),
        legend.key.height = unit(20, units = "pt")
      ) +
      ggtitle(paste(s, "| Mean 2 | Ch. 1-9 Rm")) +
      scale_fill_gradient2(low = "blue", mid = "white", high = "red", name = "Difference in means (y-x)") +
      xlab("") +
      ylab("") +
      coord_equal() +
      geom_text(aes(label = p.adj.signif))

    ggsave(
      plot = print(heatmap), filename = paste0("Outputs/pnn_analysis/heatmaps/two_cluster_gmm/mean_2/chs_removed/", s, "_mean_2_groups_ch_1_9_removed.png"),
      device = "png", width = 6, height = 6, units = "in", dpi = 600
    )

    t_tests[[s]] <- test
    heatmaps[[s]] <- heatmap
    returns[[1]] <- t_tests
    returns[[2]] <- heatmaps
    returns[[3]] <- group_variance
  }
  figure <- ggarrange(
    plotlist = heatmaps, ncol = 5,
    nrow = 5,
    align = "hv",
    common.legend = TRUE,
    legend = "right",
    labels = "AUTO"
  )

  annotated_figure <- annotate_figure(p = figure, top = text_grob("2 Cluster GMM | Mean 2 | Chs. 1-9 Removed", face = "bold", size = 18))

  ggsave(path = "Outputs/pnn_analysis/heatmaps/two_cluster_gmm/mean_2/chs_removed/", filename = "mean_2_2_cluster_gmm_combo_plot_chs_1_9_removed.png", plot = annotated_figure, device = "png", width = 20, height = 20, units = "in", dpi = 600, bg = "white")
} else if (gmm_n == 1 & chs_rm == "n" & using_mean1 == FALSE) {
  for (s in unique(icc_df$subregion)) {
    icc_df_sub <- filter(icc_df, subregion == s)
    group_variance <- fligner.test(mean_1 ~ condition, data = icc_df_sub)
    test <- t_test(
      data = icc_df_sub, formula = mean_1 ~ condition,
      p.adjust.method = "holm", conf.level = 0.999, detailed = TRUE
    )

    # Heatmap
    mid <- 0
    heatmap <- ggplot(data = test, aes(
      x = group2, y = group1,
      fill = estimate
    )) +
      geom_tile() +
      theme(
        plot.title = element_text(size = 12, face = "plain", hjust = 0.5),
        panel.background = element_blank(),
        axis.text.y = element_text(
          size = 8, face = "plain", angle = 90,
          hjust = 0.5
        ),
        axis.text.x = element_text(size = 8, face = "plain"),
        legend.key.height = unit(20, units = "pt")
      ) +
      ggtitle(paste(s, "| Mean 1")) +
      scale_fill_gradient2(low = "blue", mid = "white", high = "red", name = "Difference in means (y-x)") +
      xlab("") +
      ylab("") +
      coord_equal() +
      geom_text(aes(label = p.adj.signif))

    ggsave(
      plot = print(heatmap), filename = paste0("Outputs/pnn_analysis/heatmaps/one_cluster_gmm/no_chs_removed/", s, "_mean_1.png"),
      device = "png", width = 6, height = 6, units = "in", dpi = 600
    )

    t_tests[[s]] <- test
    heatmaps[[s]] <- heatmap
    returns[[1]] <- t_tests
    returns[[2]] <- heatmaps
    returns[[3]] <- group_variance
  }

  figure <- ggarrange(
    plotlist = heatmaps, ncol = 5,
    nrow = 5,
    align = "hv",
    common.legend = TRUE,
    legend = "right",
    labels = "AUTO"
  )

  annotated_figure <- annotate_figure(p = figure, top = text_grob("1 Cluster GMM | Mean 1", face = "bold", size = 18))

  ggsave(path = "Outputs/pnn_analysis/heatmaps/one_cluster_gmm/no_chs_removed/", filename = "mean_1_1_cluster_gmm_combo_plot.png", plot = annotated_figure, device = "png", width = 20, height = 20, units = "in", dpi = 600, bg = "white")
} else if (gmm_n == 1 & chs_rm == "y" & using_mean1 == FALSE) {
  for (s in unique(icc_df$subregion)) {
    icc_df_sub <- filter(icc_df, subregion == s)
    group_variance <- fligner.test(mean_1 ~ condition, data = icc_df_sub)
    test <- t_test(
      data = icc_df_sub, formula = mean_1 ~ condition,
      p.adjust.method = "holm", conf.level = 0.999, detailed = TRUE
    )

    # Heatmap
    mid <- 0
    heatmap <- ggplot(data = test, aes(
      x = group2, y = group1,
      fill = estimate
    )) +
      geom_tile() +
      theme(
        plot.title = element_text(size = 12, face = "plain", hjust = 0.5),
        panel.background = element_blank(),
        axis.text.y = element_text(
          size = 8, face = "plain", angle = 90,
          hjust = 0.5
        ),
        axis.text.x = element_text(size = 8, face = "plain"),
        legend.key.height = unit(20, units = "pt")
      ) +
      ggtitle(paste(s, "| Mean 1 | Ch. 1-9 Rm")) +
      scale_fill_gradient2(low = "blue", mid = "white", high = "red", name = "Difference in means (y-x)") +
      xlab("") +
      ylab("") +
      coord_equal() +
      geom_text(aes(label = p.adj.signif))

    ggsave(
      plot = print(heatmap), filename = paste0("Outputs/pnn_analysis/heatmaps/one_cluster_gmm/chs_removed/", s, "_mean_1_ch_1_9_removed.png"),
      device = "png", width = 6, height = 6, units = "in", dpi = 600
    )

    t_tests[[s]] <- test
    heatmaps[[s]] <- heatmap
    returns[[1]] <- t_tests
    returns[[2]] <- heatmaps
    returns[[3]] <- group_variance
  }

  figure <- ggarrange(
    plotlist = heatmaps, ncol = 5,
    nrow = 5,
    align = "hv",
    common.legend = TRUE,
    legend = "right",
    labels = "AUTO"
  )

  annotated_figure <- annotate_figure(p = figure, top = text_grob("1 Cluster GMM | Mean 1 | Chs. 1-9 Removed", face = "bold", size = 18))

  ggsave(path = "Outputs/pnn_analysis/heatmaps/one_cluster_gmm/chs_removed/", filename = "mean_1_1_cluster_gmm_combo_plot_chs_1_9_removed.png", plot = annotated_figure, device = "png", width = 20, height = 20, units = "in", dpi = 600, bg = "white")
} else if (gmm_n == 2 & chs_rm == "n" & using_mean1 == TRUE) {
  for (s in unique(icc_df$subregion)) {
    icc_df_sub <- filter(icc_df, subregion == s)
    group_variance <- fligner.test(mean_1 ~ condition, data = icc_df_sub)
    test <- t_test(
      data = icc_df_sub, formula = mean_1 ~ condition,
      p.adjust.method = "holm", conf.level = 0.999, detailed = TRUE
    )

    # Heatmap
    mid <- 0
    heatmap <- ggplot(data = test, aes(
      x = group2, y = group1,
      fill = estimate
    )) +
      geom_tile() +
      theme(
        plot.title = element_text(size = 12, face = "plain", hjust = 0.5),
        panel.background = element_blank(),
        axis.text.y = element_text(
          size = 8, face = "plain", angle = 90,
          hjust = 0.5
        ),
        axis.text.x = element_text(size = 8, face = "plain"),
        legend.key.height = unit(20, units = "pt")
      ) +
      ggtitle(paste(s, "| Mean 1")) +
      scale_fill_gradient2(low = "blue", mid = "white", high = "red", name = "Difference in means (y-x)") +
      xlab("") +
      ylab("") +
      coord_equal() +
      geom_text(aes(label = p.adj.signif))

    ggsave(
      plot = print(heatmap), filename = paste0("Outputs/pnn_analysis/heatmaps/two_cluster_gmm/mean_1/no_chs_removed/", s, "_mean_1.png"),
      device = "png", width = 6, height = 6, units = "in", dpi = 600
    )

    t_tests[[s]] <- test
    heatmaps[[s]] <- heatmap
    returns[[1]] <- t_tests
    returns[[2]] <- heatmaps
    returns[[3]] <- group_variance
  }
  figure <- ggarrange(
    plotlist = heatmaps, ncol = 5,
    nrow = 5,
    align = "hv",
    common.legend = TRUE,
    legend = "right",
    labels = "AUTO"
  )

  annotated_figure <- annotate_figure(p = figure, top = text_grob("2 Cluster GMM | Mean 1", face = "bold", size = 18))

  ggsave(path = "Outputs/pnn_analysis/heatmaps/two_cluster_gmm/mean_1/no_chs_removed/", filename = "mean_1_2_cluster_gmm_combo_plot.png", plot = annotated_figure, device = "png", width = 20, height = 20, units = "in", dpi = 600, bg = "white")
} else if (gmm_n == 2 & chs_rm == "y" & using_mean1 == TRUE) {
  for (s in unique(icc_df$subregion)) {
    icc_df_sub <- filter(icc_df, subregion == s)
    group_variance <- fligner.test(mean_1 ~ condition, data = icc_df_sub)
    test <- t_test(
      data = icc_df_sub, formula = mean_1 ~ condition,
      p.adjust.method = "holm", conf.level = 0.999, detailed = TRUE
    )

    # Heatmap
    mid <- 0
    heatmap <- ggplot(data = test, aes(
      x = group2, y = group1,
      fill = estimate
    )) +
      geom_tile() +
      theme(
        plot.title = element_text(size = 12, face = "plain", hjust = 0.5),
        panel.background = element_blank(),
        axis.text.y = element_text(
          size = 8, face = "plain", angle = 90,
          hjust = 0.5
        ),
        axis.text.x = element_text(size = 8, face = "plain"),
        legend.key.height = unit(20, units = "pt")
      ) +
      ggtitle(paste(s, "| Mean 1 | Ch. 1-9 Rm")) +
      scale_fill_gradient2(low = "blue", mid = "white", high = "red", name = "Difference in means (y-x)") +
      xlab("") +
      ylab("") +
      coord_equal() +
      geom_text(aes(label = p.adj.signif))

    ggsave(
      plot = print(heatmap), filename = paste0("Outputs/pnn_analysis/heatmaps/two_cluster_gmm/mean_1/chs_removed/", s, "mean_1_ch_1_9_removed.png"),
      device = "png", width = 6, height = 6, units = "in", dpi = 600
    )

    t_tests[[s]] <- test
    heatmaps[[s]] <- heatmap
    returns[[1]] <- t_tests
    returns[[2]] <- heatmaps
    returns[[3]] <- group_variance
  }
  figure <- ggarrange(
    plotlist = heatmaps, ncol = 5,
    nrow = 5,
    align = "hv",
    common.legend = TRUE,
    legend = "right",
    labels = "AUTO"
  )

  annotated_figure <- annotate_figure(p = figure, top = text_grob("2 Cluster GMM | Mean 1 | Chs. 1-9 Removed", face = "bold", size = 18))

  ggsave(path = "Outputs/pnn_analysis/heatmaps/two_cluster_gmm/mean_1/chs_removed/", filename = "mean_1_2_cluster_gmm_combo_plot_chs_1_9_removed.png", plot = annotated_figure, device = "png", width = 20, height = 20, units = "in", dpi = 600, bg = "white")
}
```
